---
name: Fernando da Silva
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: B.S. in Economics
position: Data Scientist
address: Florianópolis SC, Brazil
www: fortietwo.com
email: fernando@fortietwo.com
github: schoulten
linkedin: schoulten
headcolor: 414141
freeze: true
output: vitae::awesomecv
---

```{r setup, include=FALSE}
withr::local_locale(c("LC_TIME" = "en"))
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About me
- Experienced data scientist proficient in data pipeline development and predictive modeling, with a strong background of 4+ years in economics and finance, using R and Python.
- Passionate about delivering value and solving problems with data using analytics and data science solutions, having developed dozens of data models and products for over 2 thousand users.
- Curious, adaptable, and focused individual who enjoys taking on new challenges and creating new solutions.

# Work experience
```{r works}
library(tibble)
library(lubridate)

time <- function(start, end) {
  td <- interval(ymd(start), ymd(end)) |> as.period(unit = "year")
  
  if (td@year == 0 & td@month %in% c(0, 1)) {paste0(" · 1 mo")}
  else if (td@year == 0 & td@month > 1) {paste0(" · ", td@month, " mo")}
  else if (td@year == 1 & td@month == 0) {paste0(" · ", td@year, " yr")}
  else if (td@year == 1 & td@month == 1) {paste0(" · ", td@year, " yr ", td@month, " mo")}
  else if (td@year == 1 & td@month > 1) {paste0(" · ", td@year, " yr ", td@month, " mos")}
  else if (td@year > 1 & td@month == 0) {paste0(" · ", td@year, " yrs")}
  else if (td@year > 1 & td@month == 1) {paste0(" · ", td@year, " yrs ", td@month, " mo")}
  else if (td@year > 1 & td@month > 1) {paste0(" · ", td@year, " yrs ", td@month, " mos")}
  else ""

}

am <- tibble(
  role    = "Data Scientist",
  company = "\\href{https://analisemacro.com.br/}{Análise Macro}",
  dates   = paste0("May 2021 - Present", time("2021-05-01", Sys.Date())),
  where   = "",
  details = c(
    "Development of predictive models using statistics, econometrics and machine learning (13+ models);",
    "Development, deployment, and monitoring (4 forecasting models);",
    "Development of reports and dashboards (100+ users) using Quarto, R Markdown, Shiny, and Plotly Dash;",
    "Development of R packages with documentation (50+ users);",
    "Development of ETL and data pipelines (40+ data sources);",
    "Development of web scraping (30+ automations);",
    "Macroeconomic analysis of Brazilian data (IS curve, Phillips curve, and Taylor rule);",
    "Time series analysis using EDA, decomposition, filters, autocorrelation, seasonality, stationarity, cointegration, Box-Jenkins methodology, univariate and multivariate models, and forecasting;",
    "Classes and courses on predictive models, econometrics, forecasting, macroeconomics, time series analysis, dashboards, reports, programming with R, Python, and SQL."
    )
  )

nomura <- tibble(
  role    = "Business Intelligence Analyst",
  company = "\\href{https://www.gruponomura.com/}{Nomura}",
  dates   = paste0("Feb 2020 - Apr 2020", time("2020-02-01", "2020-05-01")),
  where   = "",
  details = c(
    "Executed Proofs of Concept (PoC), implementation and deployment of Business Intelligence projects (Power BI, Excel, R);",
    "Interface with stakeholders, internal and external data sources mapping, ETLs, dashboards development and documentation."
    )
  )

banri <- tibble(
  role    = "Intern",
  company = "\\href{https://www.banrisul.com.br/}{Banrisul}",
  dates   = paste0("Jan 2018 - Dec 2019", time("2018-01-01", "2020-01-01")),
  where   = "",
  details = c(
    "Risk analysis and credit granting for SME portfolio (credit operations, personal/real guarantees, registration, provisions, etc.);",
    "Investment and application advice (fixed income securities, investments/redemptions, simulations);",
    "Customer service and sale of financial products (individual/corporate registration, account opening, aggregation of cross-sell products)."
    )
  )

dplyr::bind_rows(am, nomura, banri) |> 
  detailed_entries(role, dates, company, where, details, .protect = FALSE)
```

# Education
```{r education}
tribble(
  ~ degree, ~ dates, ~ institution,
  "Bachelor’s in Economics", "Mar 2014 - Dec 2019", "\\href{https://www.furg.br/en/}{Federal University of Rio Grande (FURG)}",
  "Associate's in Information Technology", "Jul 2009 - Jan 2011", "\\href{https://ifmt.edu.br/}{Federal Institute of Mato Grosso (IFMT)}"
  
) %>% 
  detailed_entries(degree, dates, institution, .protect = FALSE)
```

# Portfolio
```{r portfolio}
tribble(
  
  ~ year, ~ title, ~ details, ~ url,
  
  # "2021", "Macro forecasting", "Predictive models for Brazilian macroeconomic variables.", "https://linktr.ee/schoulten",
  
  "2021", "meedr", "R client for the Central Bank of Brazil macroeconomic expectations data API.", "https://fortietwo.com/meedr/",

  "2020", "Macro View", "Brazilian macroeconomic data dashboard developed in R.", "https://fortietwo.com/macroview/",
  
  "2017", "Macro Report", "Quarterly report on the analysis of Brazil's economic situation.", "https://gecefurg.com.br/boletins/boletim-macro/"
  
  ) %>% 
  brief_entries(
    glue::glue(
      "\\textbf{<title>}: <details> \\newline \\url{<url>}", 
      .open = "<", 
      .close = ">"
      ),
    year, 
    .protect = FALSE
    )
```

\newpage
# Volunteering
```{r}
gece <- tibble(
  role    = "Macroeconomic Analyst",
  company = "\\href{https://gecefurg.com.br/}{Economic Situation Study Group (GECE/FURG)}",
  dates   = paste0("Sep 2017 - Dec 2020", time("2017-09-01", "2020-12-01")),
  where   = "",
  details = c(
    "Group co-founder, leading management activities, economic data analysis, and content creation;",
    "Quarterly publication and presentation of economic situation reports, covering monetary policy;",
    "Creation and automation of economic data reports and dashboards using the R language, Git, and GitHub."
    )
  )

aiesec <- tibble(
  role    = "Volunteer Staff",
  company = "\\href{https://aiesec.org.br/}{AIESEC}",
  dates   = paste0("Jan 2016 - Jan 2017", time("2016-01-01", "2017-01-01")),
  where   = "",
  details = c(
    "Business Development Ambassador (Aug 2016 - Jan 2017): development of the B2B area, partnership prospecting and spreading of engagement campaigns.",
    "Relationship Manager of Marketing (Jul 2016 - Jan 2017): partnership prospecting with student organizations, alumni relationship building, event organization.",
    "Operations Manager of Talent Management (Jan 2016 - Jun 2016): productivity and HR retention analysis by operation, identifying improvement gaps in sales teams, report compilation and presentation."
    )
  )

estudar <- tibble(
  role    = "Volunteer Partner",
  company = "\\href{https://www.estudar.org.br/}{Estudar Foundation}",
  dates   = paste0("Nov 2015 - Oct 2017", time("2015-01-01", "2017-01-01")),
  where   = "",
  details = c(
    'The mission of the "Leadership 16h" volunteer is to enable the realization of the course in a larger volume and quality, reinforcing the mission of the Estudar Foundation to develop a transformative leadership throughout the country. As a Partner, I worked on the promotion, sale, logistics and infrastructure of two editions in Rio Grande RS, in the years of 2015 and 2017, where we were successful in enrollments.'
    )
  )

dplyr::bind_rows(gece, aiesec, estudar) |> 
  detailed_entries(role, dates, company, where, details, .protect = FALSE)
```


# Skills
```{r}
time_year <- function(start, end = Sys.Date()) {
  x <- as.period(interval(ymd(start), ymd(end)), unit = "year")@year
  if (x %in% c(0, 1)) {paste0("1 year")}
  else if (x >= 1) {paste0(x, " years")}
  else ""
}
```

- R (`r time_year("2019-01-01")`)
- Python (`r time_year("2021-01-01")`)
- Quarto (`r time_year("2022-01-01")`)
- Git (`r time_year("2019-01-01")`)
- GitHub (`r time_year("2019-01-01")`)
- SQL (`r time_year("2022-01-01")`)


# Languages

- Portuguese (Native)
- English (Advanced)
